|

### 2025-11-07 manuscript/paper.Rmd
updated.

One and appropriate weight function was chosen, we get the following formula for weighted information:

@@

Regardless of which method one chooses for defining weights between $\hat{r}$ and $r$, a second set of weights needs to be defined because the number of teams that need to be accurately ordered differs based on the choice of salient ranks. Therefore, we define a second set of weights, $m$, which is used to indicate which ranks are salient. We call these the "salient weights" to differentiate from the other weighting function, $w$. As an example, for a four-team tournament, if the organizer decided that only the correctly choosing the best team as the winner was important, then $m = \{1,0,0,0\}$ (i.e. essentially measuring effectivity)^[7].

^[7]: One can imagine that in an event like the Olympics, the salient weights would be 1's for the first three elements and 0's elsewhere.

@@

$$
wI_m(r_{\{{i|m_i >0}\}}, \hat{r}_{\{{i|m_i >0}\}})=\sum_{r_{\{{i|m_i >0}\}}}\sum_{\hat{r}_{\{{i|m_i >0}\}}} w_m(\hat{r}_{\{{i|m_i >0}\}}, r_{\{{i|m_i >0}\}}) \times
$$

@@

Because this mutual information is unitless, the formula can be standardized to be between 0 and 1 as follows: 
$$
\frac{wI_m(r,\hat{r})}{\text{max}\{H(r), H(\hat{r})\}}
$$

>>>>

Once an appropriate weight function $w(r, \hat{r})$ is chosen, we get the following formula for weighted information:

@@

Regardless of which method one chooses for defining weights between $\hat{r}$ and $r$, a second set of weights needs to be defined because the number of teams that need to be accurately ordered differs based on the choice of salient ranks. Therefore, we define a second vector of weights, $m$, which is used to indicate which ranks are salient. We call these the "salient weights" to differentiate from the other weighting function, $w$, becomes a function of $m$ (and also, as before, $r$ and $hat{r}$).  As an example, for a four-team tournament, if the organizer decided that only the correctly choosing the best team as the winner was important, then $m = \{1,0,0,0\}$ (i.e. essentially measuring effectivity)^[7].

^[7]: One can imagine that in an event like the Olympics, the salient weights would be 1's for the first three elements and 0's elsewhere (i.e. $m = \{1,1,1,0\}$).

@@

$$
I^m_w(r,\hat{r})= \sum_{r}\sum_{\hat{r}}w(r, \hat{r}, m)p(r,\hat{r})\log \frac {p(r,\hat{r})}{p(r)p(\hat{r})}
$$
.

If we choose to use the weighted Kendall's $\tau$ for our weights, $w(r, \hat{r}, m)$ would be:

$$
w(r, \hat{r}, m) = \frac{\sum_{i \ne j} m^{\star}_{ij}\text{sign}_{(0+)}(r_i - r_j)sign_{(0+)}(\hat{r}_i - \hat{r}_j)}{\sum_{i,j}m^{\star}_{i,j}- \sum_i m^{\star}_{i,i}}
$$
where $m^{\star}_{i,j} = m_{min(i,j)}$ and $sign_{(0+)}(.)$ is the sign of the input with the special case that a 0 maps to 1.

<!-- $$ -->
<!-- wI_m(r_{\{{i|m_i >0}\}}, \hat{r}_{\{{i|m_i >0}\}})=\sum_{r_{\{{i|m_i >0}\}}}\sum_{\hat{r}_{\{{i|m_i >0}\}}} w_m(\hat{r}_{\{{i|m_i >0}\}}, r_{\{{i|m_i >0}\}}) \times -->
<!-- $$ -->

@@

Because this mutual information is unitless, the formula can be standardized to be between 0 and 1 as follows: 
$$
\frac{I^m_w(r,\hat{r})}{\text{max}\{H(r), H(\hat{r})\}}
$$
